### 2016-08-31 doc/publications/plos16/plos16.tex
added timings to plos16.tex

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{Method} & \bf{Error (ARI)} & \bf{Runtime} & \bf{Memory/Node} \\
\hline

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & CursedForest & 0.077 (XX)  &  &  \\
& RF - Spark ML &  &  &  \\
& RF - R & 0.456 & 2.89 & 18GB \\ \hline

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364} & CursedForest & 0.063 (XX) & 1hr 58min & 4GB \\
& RF - Spark ML & 0.94 & 8hr 29min & 8GB \\
& LR - Spark ML&  & 2hr 6min & 8GB\\ \hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051}  & CursedForest & 0.046 (XX) & 4hr 0min & 4GB\\
& RF - Spark ML & &  &\\
& LR - Spark ML & & 14hr 48min & 8GB \\ \hline

@@

\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

>>>>

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
\bf{Genome \%}  & \bf{Method} & \bf{Error (ARI)} & \bf{Runtime} & \bf{Memory/Node} \\
\hline

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & CursedForest & 0.077 (XX)  &  &  \\
& RF - Spark ML &  &  &  \\
& RF - R &  0.05  & 24 min  & 18GB\footnote{using the \texttt{parallel} packages with 10 nodes}\\
& ranger -R &         0.05 &        1 min 10 seconds  &          16GB  (one processor) \\
 \hline
\multirow{3}{*}{phase3\_chr22: 2,504 x 1,103,548} &  &  &  &  \\
& RF - R & NA  & NA & NA\footnote{long vectors ($> 2^31-1$)  are not supported in the .Fortran interface}\\
&  H2O   &        0.05 &     16 hours       &   600GB \footnote{java -Xmx600g -jar h2o.jar,   h2o.init(nthreads=20)} \\
\hline
\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364} & CursedForest & 0.063 (XX) & 1hr 58min & 4GB \\
& RF - Spark ML & 0.94 & 8hr 29min & 8GB \\
& LR - Spark ML&  & 2hr 6min & 8GB\\ 
& ranger  R   &  0.06   &     28 mins  &            num.threads=10\footnote{don't know how to get the memory used, This
  was done on dpas-03} \\ 
\hline
\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051}  & CursedForest & 0.046 (XX) & 4hr 0min & 4GB\\
& RF - Spark ML & &  &\\
& LR - Spark ML & & 14hr 48min & 8GB \\ 
& ranger  R   &  0.05   &     58 mins\footnote{ but took 6 hours to load the data}  &      909GB\footnote{I think this is total memory. The job was run with
  ntasks-per-node=160 cores-per-socket=10 on ruby }  \\ 
\hline

@@

\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{minipage}
\end{table}
